Optimized Synthesized Spectrum

### 2016-10-01 2016.10.3 Jason_v2.tex
Add files via upload

\title{Optimized Synthesized Spectrum}% Force line breaks with \\
\thanks{A footnote to the article title}%

\author{Jason Cao}
 \altaffiliation[Also at ]{Physics Department, New York University.}%Lines break automatically or can be forced with \\

@@

\item[Structure]
The first part describes how to synthesize the spectrum from the Cannon 2. The second part talks about how to optimize the method and generate a better synthesized spectrum. Finally, we compare the results .
\end{description}
\end{abstract}

@@

\section{\label{sec:level1}Infer spectrum by using the Cannon 2}

@@

 This is how to obtain the synthesized spectrum by using the Cannon 2.

 \bigskip
 The code is as followed:

@@

 \bigskip
v = model.vectorizer.get\_label\_vector(inferred\_labels)

 \bigskip
inferred\_flux = np.dot(v,model.theta.T)

 \section{\label{sec:level1}optimize the inferred spectrum}

@@

\[y_{j,n}^{optimized}=a\cdot y_{j-1,n}^{inferred}+b\cdot y_{j,n}^{inferred}+c\cdot y_{j+1,n}^{inferred}(2)\]
\bigskip

Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. 
a+b+c should be equal to 1.
\bigskip

@@

\bigskip

@@

parameters are a, b and c
\bigskip

The result is \(a+b+c = 0.983661295269\). To make a+b+c=1, set a = a/(a+b+c)

b = b/(a+b+c) c = c/(a+b+c)

Calculate the optimized spectrum \( y_{j,n}^{optimized}\) by using (2)

@@

 \section{\label{sec:level1}Compare the two methods.}

@@

\includegraphics[width=70mm]{figure_1.png}

 Then compare the chi-square for a random stellar of the two methods:
 chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are 145.84 and 145.89
 They are similar to each other.

>>>>

\title{Optimized Synthesized Spectrum}% Force line breaks with \\

\author{Jason Cao}

@@

\item[Structure]
There are four sections. The first part is the introduction part, which describes the background of the method. Then in the assumptions and method part, we show the detail of our method. The next section is the experiment, where the experiment results are showed. Finally, we discuss our results?
\end{description}
\end{abstract}

@@

\section{\label{sec:level1}Introduction}

Coming soon...

 \section{\label{sec:level1}Assumption and method}

@@

 This is how to obtain the synthesized spectrum by using the Cannon 2.
 The code is as followed:

@@

 \bigskip
v = model.vectorizer.get\_label\_vector(inferred\_labels)
\bigskip

inferred\_flux = np.dot(v,model.theta.T)
 \bigskip

@@

\[y_{j,n}^{optimized}=a\cdot y_{j-1,n}^{inferred}+b\cdot y_{j,n}^{inferred}+c\cdot y_{j+1,n}^{inferred}(2)\]

Then fit \(y_{j,n}^{optimized} \) with \(y_{jn}\), where \(y_{jn}\) is the spectrum data for star n at wavelength pixel j. The optimization method we use is Levenberg - Marquardt algorithm.
a+b+c should be equal to 1.

@@

@@

parameters are a, b and c

The result is \(a+b+c = 0.983661295269\). (a,b,c) = (0.338, 0.110, 0.536)

Calculate the optimized spectrum \( y_{j,n}^{optimized}\) by using (2)
\bigskip

If the optimization works, we will optimized \(\theta_{j}\) besides a,b and c, which will come soon.

@@

 \section{\label{sec:level1}Experiment}
 \subsection{\label{sec:level2}Experiment 1}

 Choose stellar aspcapStar-v304-2M16421116+361822
 5. Then plot the spectrum

@@

%\includegraphics[width=70mm]{figure_1.png}

 Then compare the chi-square for aspcapStar-v304-2M16421116+3618225 of the two methods:
 chi-square for \( y_{j,n}^{inferred}\) and \( y_{j,n}^{optimized}\) are 145.84 and 145.89
 They are similar to each other.

 %% Fourth paragraph

 \section{\label{sec:level1}Discussion}

 Coming soon.
